White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-09-10 papers/wdmerger_II/paper.tex
Add comment on aprox19 and aprox21 failures

>>>>

\aproxnineteen\ and \aproxtwentyone\ both take significantly longer to evaluate at our default
ODE tolerances than \aproxthirteen\ does, even after accounting for the increased number of species.
This is due to a significant number of integration failures and subsequent retries (see the discussion
in \autoref{sec:burner}). The species tolerance of $10^{-8}$ is challenging for these networks.
